Target Readability in Interpersonal Accuracy

### 2022-05-16 manuscript.Rmd
move data merge to main and upload data for affect

# import data
df <- rio::import(here::here("data", "df.csv"))
```

@@

@@

summary(SAM1)
(SAM1)

>>>>

# import data for exploratory predictors
paths <- dir_ls(here("data"))
df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)

walk2(df_names, paths, ~{
  assign(.x, import(.y), envir = .GlobalEnv)
})

# Make variable types/names congruent for merging
# rename
ind_diffs_self %<>% 
  rename(PerUn = SubNum)

old_names <- names(raw_informant_data[,44:189])
new_names <- paste0(names(raw_informant_data[, 44:189]), "_inf")

raw_informant_data %<>% 
  rename_at(vars(old_names), ~ new_names)

# remove
ind_diffs_self %<>% 
  select(-sex:-strait26,
         -Perceiver, -Target)

raw_informant_data %<>% 
  select(-Perceiver,
         -name:-V3)

# bfi
informant_bfi <- 
  raw_informant_data %>% 
  select(PerUn, starts_with("bfi")) %>% 
    group_by(PerUn) %>% 
    summarise(across(bfi1:bfi26, 
                     mean, na.rm = TRUE)
              ) %>% 
    ungroup() %>% 
    rename_at(vars(bfi1:bfi26), ~ paste0("itrait", 1:26)
              )
# Merge
df <- list(perceiver_target_data,
           perceiver_target_affect_EA,
           ind_diffs_self,
           informant_bfi,
           aggregated_informant_data) %>% 
  reduce(left_join)

rm(list = gdata::keep(df))
```

@@

```{r}
# affect
samEACaggdata <- rio::import(here::here("data", "samdata.csv"))

@@

sjPlot::tab_model(SAM1)

## save random effects
lapply(ranef(SAM1), write.table, 
       append = TRUE, 
       file = here::here("data", "raneff from SAM1 for TRT.csv"))

## extract empirical bayesian estimates for targets
EBTRTtar <- ranef(SAM1)$TarUn
colnames(EBTRTtar)<-c("Intercept","TSR","Norm")
EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
map_dbl(EBTRTtar, sd)

## extract empirical bayesian estimates for perceivers
EBTRTper <- ranef(SAM1)$PerUn
EBTRTper$PerUn<-as.numeric(row.names(EBTRTper))
map_dbl(EBTRTper,sd)

## Density plots for random effects will be here
